|

### 2020-06-13 appendix/appendix_final.Rmd
commit graphs and finishing appendix 1

---
title: "Appendix"
author: "Umberto Mignozzetti"
date: "12/25/2019"
header_includes:
- \usepackage{booktabs}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output: pdf_document
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r global_options, include=FALSE}
## Starting
set.seed(732578) # From random.org

@@

```

## Search criteria

@@

We webscraped the main databases in Social Sciences: \href{https://scholar.google.com/}{Google Scholar} (n = 1001); \href{https://academic.microsoft.com/home}{Microsoft Academic} (n = 927); and
\href{https://www.scopus.com/}{Scopus} (n = 736). The R script we wrote extracted, to a .csv file, the title, abstract, authors, year, journal of publication, and database from which the record originated. We screened these results with an English language and Article restriction -- meaning, we excluded all records written in other languages and all that were not academic papers, such as book chapters, doctoral theses, etc. We set no restriction to unpublished articles.

Below, you will find the webscrape script:

``` {r, eval = FALSE}

#### INSTALLING PACKAGES ####

install.packages('tidyverse')
install.packages('rvest')
install.packages('RSelenium')

#### LOADING PACKAGES ####

library(tidyverse)
library(rvest)
library(RSelenium)

# site: https://scholar.google.com

remDr$navigate("https://scholar.google.com/
               scholar?cites=13117579863846712459&as_sdt=2005&sciodt=0,5")

  # Changing Pages
  next_button <- remDr$findElement(using = "xpath", "/html/body/div/div[11]/div[2]/div[2]/div[3]/
                                   div[2]/center/table/tbody/tr/td[12]/a/b")
  next_button$clickElement()

  # Deleting cookies
  remDr$deleteAllCookies()
}

# Scraping Scopus requires a bit more manual labor.
# You can login on scopus through your university/institution and download the metadata
#o fthe article(s) you want directly from there.
# All we need to do after that is scrape the information of
# every link from the .csv file downloaded previously

# url: https://academic.microsoft.com/home

articles <- list()
k <- 0
remDr$navigate("https://academic.microsoft.com/paper/
               2076316673/citedby/search?q=The%20Political%
               20Economy%20of%20Benefits%20and%20Costs%3A%20A%
               20Neoclassical%20Approach%20to
               %20Distributive%20Politics&qe=RId%253D2076316673&f=&orderBy=0")

write_csv(articles_links, "microsoft_academic_clean.csv")

```

## Article Selection

@@

#### Exclusion analysis

@@

1. Matched treatment variable:
  + N: Number Legislators Lower House
  + logN: Log Number Legislators Lower House
  + K: Number Legislators Upper House

2. Matched outcome variable:
  + ExpPC: Expenditure Per Capita
  + logExpPC: Log Expenditure Per Capita
  + PCTGDP: Percent GDP Public Expenditure

### Flow Chart

@@

 \end{tikzpicture}

```

## Meta-analysis dataset

@@

```{r, echo=FALSE, include=FALSE}

# Paper 367
dat <- data.frame(
  id = 367,
  published = 'Yes',
  usemeta = 1,
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Spatially Targeted Government Spending and
Heterogeneous Constituent Cost Shares',
  author = 'Bradbury and Stephenson',
  year = 2009,
  authoryear = 'Bradbury and Stephenson (2009)',
  journal = 'The Journal of Private Enterprise',
  web = 'http://journal.apee.org/index.php?title=Spring2009_6',
  table = 2,
  column = 2,
  indepvar = 'MEMSENATE',
  indepvar2 = 'K',
  depvar = 'Total Spending per capita',
  depvar2 = 'ExpPC',
  coef = 0.624,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.624/3.10
)

# Paper 585 K
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 5,
  indepvar = 'Upper size',
  indepvar2 = 'K',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.01262,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.01262/2.12
))

# Paper 585 K
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 2,
  indepvar = 'Upper size',
  indepvar2 = 'K',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.004964,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.004964/2.9
))

# Paper 585 K
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 3,
  indepvar = 'Upper size',
  indepvar2 = 'K',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = -0.01134,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.01134/4.52
))

# Paper 585 K
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 4,
  indepvar = 'Upper size',
  indepvar2 = 'K',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = -0.00559,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.00559/2.39
))

# Paper 585 N
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 5,
  indepvar = 'Lower size',
  indepvar2 = 'N',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.003627,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.003627/2.51
))

dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 2,
  indepvar = 'Lower size',
  indepvar2 = 'N',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.000517,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.000517/0.47
))

dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 3,
  indepvar = 'Lower size',
  indepvar2 = 'N',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.016946,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.016946/8.65
))

dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 4,
  indepvar = 'Lower size',
  indepvar2 = 'N',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.012337,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.012337/6.65
))

# Paper 505
dat <- rbind(dat,
  data.frame(
  id = 505,
  published = 'Yes',
  usemeta = 1,
  method = 'IV',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The Endogeneity of the Initiative: A Comment on Marschall and Ruhil',
  author = 'Matsusaka',
  year = 2005,
  authoryear = 'Matsusaka (2005)',
  journal = 'State Politics & Policy Quarterly',
  web = 'https://www.jstor.org/stable/40421558',
  table = 1,
  column = 3,
  indepvar = 'Seats',
  indepvar2 = 'N',
  depvar = 'State Government Expenditure per Capita',
  depvar2 = 'ExpPC',
  coef = -0.96,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.18
))

# Paper 448
dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 1,
  method = 'IV',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 4,
  column = 1,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.213,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.018
))

# Paper 448
dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'IV',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 4,
  column = 2,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.229,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.037
))

# Paper 448
dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'IV',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 4,
  column = 3,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.455,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.038
))

# Paper 448
dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'IV',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 4,
  column = 4,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.411,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.049
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 1,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.226,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.053
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 2,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.213,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.317
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 3,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.185,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.305
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 4,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.235,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.336
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 5,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.374,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.064
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 6,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.811,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.181
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 7,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.795,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.176
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 8,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.849,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.238
))

dat <- rbind(dat,
  data.frame(
  id = 974,
  published = 'No',
  usemeta = 1, 
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'Latin America',
  title = 'Institutional arrangements and fiscal performance: the latin american experience',
  author = 'Stein, Talvi, and Grisanti',
  year = 1998,
  authoryear = 'Stein et al. (1998)',
  journal = 'NBER Working papers',
  web = 'https://www.nber.org/papers/w6358.pdf',
  table = 3,
  column = 1,
  indepvar = 'District magnitude',
  indepvar2 = 'logN',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.0109,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.0143
))

dat <- rbind(dat,
  data.frame(
  id = 974,
  published = 'No',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'Latin America',
  title = 'Institutional arrangements and fiscal performance: the latin american experience',
  author = 'Stein, Talvi, and Grisanti',
  year = 1998,
  authoryear = 'Stein et al. (1998)',
  journal = 'NBER Working papers',
  web = 'https://www.nber.org/papers/w6358.pdf',
  table = 3,
  column = 4,
  indepvar = 'District magnitude',
  indepvar2 = 'logN',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.0135,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.0121
))

>>>>

---
title: |
       | Supplementary Materials for "The Effect of Legislature Size on Public Spending: A Meta-Analysis"
author: 
- "Huzeyfe Alptekin[^alptekin]"
- "Danilo Freire[^freire]"
- "Umberto Mignozzetti[^mignozzetti]"
- "Catarina Roman[^roman]"
date: June 13, 2020
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

\appendix

[^alptekin]: Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Getulio Vargas Foundation, Brazil, <huzeyfealptekin@gmail.com>.

[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, <danilofreire@brown.edu>, <http://danilofreire.github.io>.

[^mignozzetti]: School of International Relations, Fundação Getulio Vargas, São Paulo, SP, Brazil and Wilf Family Department of Politics, NYU, NY, USA, <umberto.mig@nyu.edu>, <http://umbertomig.com>.

[^roman]: Research Associate, Department of International Relations, Getulio Vargas Foundation, Brazil, <catarinamroman@gmail.com>.

```{r, include=FALSE}
# Knitr options
knitr::opts_chunk$set(fig.pos = 'H') # holds figure position
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
## Starting
set.seed(732578) # From random.org

@@

# Build plot function for forest plots
build_forest <- function(mod, capt, lsize = 22, ttl = NULL) {
  # Build dataset for plot
  mod2 <- tibble(
    TE = mod$TE,
    seTE = mod$seTE,
    studlab = mod$studlab,
    lower = mod$lower,
    upper = mod$upper,
    group = "A") %>%
    bind_rows(.,
              aux = tibble(
                TE = c(mod$TE.random, NA),
                seTE = c(mod$seTE.random, NA),
                studlab = c("Overall Effect", "Prediction Interval"),
                lower = c(mod$lower.random, mod$lower.predict),
                upper = c(mod$upper.random, mod$upper.predict),
                group = "B")) %>%
    group_by(studlab) %>%
    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
    ungroup()

  # Graph limits
  limg <- max(abs(c(mod2$lower, mod2$upper)))

  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab2,TE), 
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group), height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits=c(-1.1*limg, 1.1*limg)) +
    scale_y_discrete(
      labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
    geom_vline(xintercept=0, 
               color="#000000", linetype="dashed") +
    labs(x = "",
         y = "") + 
    facet_grid(group~., scales = "free", space = "free") + 
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8*lsize, 
                                     hjust = 1),
          axis.text.x = element_text(size = .6*lsize, 
                                     hjust = 1.1),
          plot.caption = element_text(size=lsize),
          plot.title.position = 'plot', 
          plot.title = element_text(hjust = 0.5, 
                                    face = 'bold',
                                    margin=margin(0,0,10,0)),
          panel.grid.major = element_blank())
  return(p)
}
```

# Search criteria

@@

We webscraped the main databases in Social Sciences: \href{https://scholar.google.com/}{Google Scholar} (n = 1001); \href{https://academic.microsoft.com/home}{Microsoft Academic} (n = 927); and \href{https://www.scopus.com/}{Scopus} (n = 736). The R script we wrote extracted, to a CSV file, the title, abstract, authors, year, journal of publication, and database from which the record originated. We screened these results with an English language and Article restriction -- meaning, we excluded all records written in other languages and all that were not academic papers, such as book chapters, doctoral theses, etc. We set no restriction to unpublished articles.

# Article Selection

@@

## Exclusion analysis

@@

1. Matched treatment variable:
  + *N*: Number Legislators Lower House
  + *logN*: Log Number Legislators Lower House
  + *K*: Number Legislators Upper House

2. Matched outcome variable:
  + *ExpPC*: Expenditure Per Capita
  + *logExpPC*: Log Expenditure Per Capita
  + *PCTGDP*: Percent GDP Public Expenditure

## Flow Chart

@@

 \end{tikzpicture}
```

# Meta-analysis dataset

@@

```{r, echo=FALSE, include=FALSE}
load('../dataset/dataCoefs.RData')
```

# Descriptive statistics

In this section, we present the descriptive statistics for our meta-analytic sample. We focus in the following paper characteristics: study year, whether the paper has been published or not, the three dependent variables of interest, the three independent variables of interest, and a few statistics about the coefficients. We also add a descriptive statistics table, similar to the one in the main paper.

## Study Year

For study year, we have an average of `r round(mean(dat$year), 2)`, with standard deviation of `r round(sd(dat$year), 2)`. The oldest study included in the paper is dated from `r min(dat$year)`, while the most recent paper is dated from `r max(dat$year)`. Therefore, we cover `r max(dat$year)-min(dat$year)` years of tests of the 1/n hypothesis.

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Study Year Frequencies"}
dat %>%
  select(id, year) %>%
  unique() %>%
  ggplot(aes(x = as.factor(year))) + 
    geom_bar(color = "black") + 
  labs(x = "",
       y = "") + 
  theme_bw()
```

## Frequency of Published Papers

We decided to report studies regardless of their publication status. From the `r length(unique(dat$id))` papers in the sample, `r as.numeric(table(unique(select(dat, id, published))$published)[1])` were published while `r as.numeric(table(unique(select(dat, id, published))$published)[2])` were not published.

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Was the study published?"}
dat %>%
  select(id, published) %>%
  unique() %>%
  ggplot(aes(x = as.factor(published))) + 
    geom_bar(color = "black") + 
  labs(x = "Published study?",
       y = "") + 
  theme_bw()
```

## Electoral system

There are many differences in the papers relative to the research design. One remarkable difference is the application of the theory, that was build with majoritarian systems in mind, in non-majoritarian democracies. In our sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])` of the papers study *Majoritarian* systems while `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study *Non-Majoritarian* electoral systems.\footnote{Note that the argument for working in a non-majoritarian system, we need to assume that despite the fact that politicians are able to campaign in every place in the district, the votes are geographycally concentrated. The concentration facilitates politicians to use pork-barrel project to captivate their electoral supporters.}

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Electoral Systems"}
dat %>%
  select(id, elecsys2) %>%
  unique() %>%
  ggplot(aes(x=as.factor(elecsys2))) + 
    geom_bar(color = "black") + 
  labs(x = "Electoral Systems",
       y = "") + 
  theme_bw()
```

## Aggregation Level

The aggregation level is also an important characteristic of the empirical tests of the law of 1/n. The model was build to explain the dynamics of majoritarian countries, but the theory was tested in municipal, county, states, and country levels. In our sample, `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[1])` studied *local* level (municipalities and counties), `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[2])` studied *State* (or Provincial) levels, and `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[3])` studied *Country* level data.

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Sample Aggregate Level"}
dat %>%
  select(id, agglevel) %>%
  unique() %>%
  ggplot(aes(x=as.factor(agglevel))) + 
    geom_bar(color = "black") + 
  labs(x = "Sample Aggregate Level",
       y = "") + 
  theme_bw()
```

## Geographical Location

The geographical location also varies considerably in the sample. In our sampled papers, `r as.numeric(table(unique(select(dat, id, location2))$location2)[1])` studied a given country, while `r as.numeric(table(unique(select(dat, id, location2))$location2)[2])` used a cross-country design, with more than one country.

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Geographical Location"}
dat %>%
  select(id, location2) %>%
  unique() %>%
  ggplot(aes(x=as.factor(location2))) + 
    geom_bar(color = "black") + 
  labs(x = "Geographical Location",
       y = "") + 
  theme_bw()
```

## Dependent variables

The outcome variables included in the paper were:

- `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[1])` Per Capita Expenditure papers
- `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[3])` Natural Log of Per Capita Expenditure papers
- `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[2])` Expenditure as a Percentage of the GDP papers

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Dependent variables across the law of 1/n studies"}
dat %>%
  select(id, depvar2) %>%
  unique() %>%
  mutate(depvar2 = factor(depvar2, 
                          labels = c("Per Capita Expenditure",
                                     "Percentage GDP Government Expenditure",
                                     "Log Per Capita Expenditure"))) %>%
  ggplot(aes(x = depvar2)) +
    geom_bar(color = "black") + 
  labs(x = "Dependent Variables",
       y = "") + 
  coord_flip() + 
  theme_bw()
```

## Independent variables

Most of papers in our meta-analytic sample study the number of legislators in the lower house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[2])`). The second most frequent independent variable is the number of legislators in the upper house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[1])`). Finally, the minority of papers study the Natural Log of the number of legislators in the lower house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[3])`). Some papers had multiple coefficients, and thus the total number of coefficients is 36, while the number of papers is only 26.

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Independent variables across the law of 1/n studies"}
dat %>%
  select(id, indepvar2) %>%
  unique() %>%
  mutate(indepvar2 = factor(indepvar2, labels = c('K (upper house legislators)',
                                                  'N (lower house legislators)',
                                                  'Log N'))) %>%
  ggplot(aes(x = indepvar2)) + 
    geom_bar(color = "black") + 
  labs(x = "Independent Variables",
       y = "") +
  coord_flip() +
  theme_bw() 
```

## Histogram of the Coefficients and the Standard Errors

The coefficients in the papers present a striking variability. In this section, we plot a histogram of the coefficients for all measurements included in the meta-analytic dataset.

```{r, echo=FALSE}
dat %>%
  ggplot(aes(x = coef)) +
  geom_histogram(bins = 15, color = "black") + 
  labs(x = "Coefficients") + 
  theme_bw()
dat %>%
  ggplot(aes(x = SE)) +
  geom_histogram(bins = 10, color = "black") + 
  labs(x = "Standard Errors") + 
  theme_bw()
```

## Sign Coefficients

One simple statistic that we can compute to access the law of 1/n is the frequency of positive and negative estimates. Below we plot the frequency for all the papers included in the meta-analytic dataset.
